% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}
\begin{projects}
  \project
    {Web based FACTOTUM Suite}{Nov 2019 - Present}
    {\website{http://cogmac.com/factotum.html}{Read more on Factotum Suite}\website{https://drive.google.com/file/d/1QNbvhu1IOR6ouCZ_UrBvNbSx-dzfLgUy/view?usp=sharing}{Presentation}}
    {$\bullet$ A low-latency web based professional trading suite. $\bullet$ Leading a team of five $\bullet$ Responsible for UI/UX designing, ideation, strategy making, \& product development $\bullet$ Handled corporate presentations \& communication.}
    {Figma, Adobe XD, PowerPoint, MS Word, Corporate communication}
  \project
    {FACTOTUM Retail}{Dec 2019 - Present}
    {\website{http://cogmac.com/factotum.html}{Read more on Factotum Retail}\website{https://drive.google.com/file/d/17qKEx1DOXvp5mXQ8woNv9X5WUxekcGYc/view?usp=sharing}{Presentation} \website{https://drive.google.com/file/d/1XTGzi8ScUTEUY15ZtxjwHEj0bkaTcoqf/view?usp=sharing}{Market Research}}
    {$\bullet$ A web and mobile app based lite trading platform. $\bullet$ Leading a team of five $\bullet$ UI/UX \& motion designing, strategy making, market research, product development etc. $\bullet$ Presented product advancements \& features to clients at meetings \& expositions.}
    {Figma, Adobe XD, PowerPoint, MS Word, Corporate Communication}
    \project
    {FACTOTUM Retail}{Dec 2019 - Present}
    {\website{http://cogmac.com/factotum.html}{Read more on Factotum Retail}\website{https://drive.google.com/file/d/17qKEx1DOXvp5mXQ8woNv9X5WUxekcGYc/view?usp=sharing}{Presentation} \website{https://drive.google.com/file/d/1XTGzi8ScUTEUY15ZtxjwHEj0bkaTcoqf/view?usp=sharing}{Market Research}}
    {$\bullet$ A web and mobile app based lite trading platform. $\bullet$ Leading a team of five $\bullet$ UI/UX \& motion designing, strategy making, market research, product development etc. $\bullet$ Presented product advancements \& features to clients at meetings \& expositions.}
    {Figma, Adobe XD, PowerPoint, MS Word, Corporate Communication}
    
    \project
    {Spreadsheet based automatic stock-watchlist parameter tracking, analysis, screeener, and alert system}{March 2020 - April 2020}
    {\website{https://drive.google.com/open?id=1Yx19fERoN-4UPaPqM6QVjLWRDGNuFuWj}{Explore here}\website{https://drive.google.com/open?id=1Yx19fERoN-4UPaPqM6QVjLWRDGNuFuWj}{Presentation}}
    {$\bullet$ A spreadsheet based any stock tracking suit, that not just tracks it's price, but also any X-day moving average, it's any X-day charts, sparklines, tracks \textit{price-above-MA} type breakoutsm ALL AUTOMATICALLY IN REAL TIME (with a 20 min lag) $\bullet$ The psreadsheet has a screener interface, that screens day's top gainers and losers, top/bottom value stocks, stocks that shows bullish/bearish-ness, 52 week high/low breaker, and many more such screeners, with with a button's click away, all in real time.  $\bullet$ My spread sheets not just displays the real-time data and tracks all your screens. Whenever you are away from your latop or not trackign your stocks movement, and one of your many alert criterion is hit, it will send you an email automatically.}
    {MS excel. Macros, VBA, Automatic emailing, Magic-cell, Fundamental Analysis, Data Analysis}
    
     
    \project
    {Spreadsheet based automatic stock-watchlist parameter tracking, analysis, screeener, and alert system}{March 2020 - April 2020}
    {\website{https://drive.google.com/open?id=13DiWTzeWzPQQ4ip6YL6HfERC7o3YAHou}{Explore here}\website{https://drive.google.com/open?id=13DiWTzeWzPQQ4ip6YL6HfERC7o3YAHou}{Presentation}}
    {$\bullet$ A spreadsheet based any stock tracking suit, that not just tracks it's price, but also any X-day moving average, it's any X-day charts, sparklines, tracks \textit{price-above-MA} type breakoutsm ALL AUTOMATICALLY IN REAL TIME (with a 20 min lag) $\bullet$ The psreadsheet has a screener interface, that screens day's top gainers and losers, top/bottom value stocks, stocks that shows bullish/bearish-ness, 52 week high/low breaker, and many more such screeners, with with a button's click away, all in real time.  $\bullet$ My spread sheets not just displays the real-time data and tracks all your screens. Whenever you are away from your latop or not trackign your stocks movement, and one of your many alert criterion is hit, it will send you an email automatically.}
    {MS excel. Macros, VBA, Automatic emailing, Magic-cell, Fundamental Analysis, Data Analysis}
   \project   
    {Cogmac's Website}{Nov 2019 - Feb 2020}
    {\website{http://www.cogmac.com}{http://www.cogmac.com} \website{https://github.com/idebdipta/CogmacWebsite}{Github Link}}
    {$\bullet$Designed and developed 6 pages $\bullet$ Prepared and edited contents $\bullet$ Github link doesn't include company sensitive contents.}
    {HTML, CSS, JavaScript}
    \project
    {IBM Data Science Capstone Project}{Oct 2019 - Dec 2019}
    {\website{https://github.com/idebdipta/IBMCapstone}{IBM Capstone on Github} \website{https://drive.google.com/file/d/1jWjhYbUrphCxf3NFJqy2Ey-RYiCxbL69/view?usp=sharing}{Presentation} }
    {$\bullet$ Data Segmentation, Data Clustering, Data Analysis, Data Visualization etc. has been exploited to find similar neighbourhood.}
    {Python, MySQL, Data Analysis, PowerPoint, Foursquare API}
    
   \project
    {Mathematical Modeling}{April 2017- June 2017}
    {\website{https://arxiv.org/abs/1502.04166}{Arxiv} \website{https://drive.google.com/file/d/156YblduI4mXih_kiLyCzyZp3D9_CJwhG/view?usp=sharing} {Presentation} \website{https://www.cta-observatory.org}{About CTA}}
    {$\bullet$ Constraining the extragalactic background light in optical and infrared spectrum by GeV and TeV Gamma-Ray attenuation. $\bullet$ Useful for finding the birth-rate of stars in different galactic era. $\bullet$ Project to serve theoretical foundation for Cherenkov Telescope Array}
    {C, ROOT, Mathematical Modeling, Data Analysis, Python}
    
   \project   
    {Personal Website and CV development}{Jan 2020 - Present}
    {\website{https://www.debdiptabiswas.com}{debdiptabiswas.com} \website{https://www.overleaf.com/read/cwfzhgqcmhmn}{CV project in Overleaf}}
    {$\bullet$ Web-design and development $\bullet$ Website management and content writing  $\bullet$ Documentation in Latex}
    {Wix, HTML, CSS, AJAX, LaTex, Overleaf}
        
\end{projects}