% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {March 2019}      {Financial Research Analyst}{COGMAC TECHNOLOGIES}{Noida}
    {Present} {
                      \begin{itemize}
                        \item \textbf{Managing Project FACTOTUM:} FACTOTUM is an advanced low-latency app based professional trading suite. Responsible for designing, ideation, strategy making, product creation and management. Management of the Web App and Android App development processes, UI/UX designing, and product presentation to potential clients.
                        
                        \item \textbf{Managing Project FACTOTUM Retail:} FACTOTUM retail is an easy to use retail oriented trading application. Responsible for designing, ideation, strategy making, and . Management of the Web App and Android App development processes, UI/UX designing, and product presentation to potential clients.
                        \item Perform secondary research on Derivatives, Greeks, Derivatives Strategie, HFT strategies.                   
                        \item Regular trading activities on company's advanced algo trading \& low latency platform FACTOTUM.
     Implemented Option strategies (e.g. Strangle, Butterfly, Box, F2F Spread etc.) and custom strategies of the company.                
                        \item Implemented different quantitative trading strategies based on Greeks, Volatility, \&   Arbitraging strategies. 
                        
                        \item Written full OMS,RMS,and Client platform documentation of the company's algo-trading suite.
                        
                        \item Performed through market research of various trading platforms for company's new retail focused trading platform - designed and ideated all components of the trading platform.
                        
                        \item Presented various research outcomes ot internal team, top management, as well as CEOs, MDs, of partner companies.
                        
                      \end{itemize}
                    }
                    {Apache Tomcat, IntelliJ Idea, Eclipse, Maven, Spring Boot, Jenkins, Nexus}
  \emptySeparator
  \experience
    {January 2019}   {Research Analyst (finance) intern}{Cogmac Technologies}{Noida}
    {March 2019}    {
                      \begin{itemize}
                        \item Developed several empirical Option pricing models based on Nifty and Bank Nifty data.                          
                        \item Backtested our empirical models with different Option trading strategies in FACTOTUM.                        
                        \item Performed thorough research literature study of Option pricing models (e.g. Black-Scholes, Merton, Cox-Ross-Rubinstein, Bakshi-Cao-Chen etc.) as well as Greeks, Volatility, I.V. etc. based strategies; presented the outcome.
                        \item Performed Monte Carlo simulation on Black-Scoles-Merton and Bakshi-Cao-Chen's formula.               
                        \item In hand experience of derivatives trading using arbitraging techniques with algo-trading suite. Deployed several strategies like Butterfly, Conversal Reversal, Straddles, Box etc.
                    \end{itemize}
                    }
                    {JBoss EAP, IntelliJ Idea, Eclipse, Maven}
  \emptySeparator
  \experience
    {January 2018}     {Management of personal and family portfolio}{}{}
    {Present}    {
                      \begin{itemize}
                        \item Fundamental Fundamental Analysis: Financial statement analysis, ratio analysis, stock price valuation methods: DCF, DDM, \& P/E based models, qualitative analysis, and basic macro analysis. 
                        \item Technical Analysis: Knowledge of charts (Candle stick, Renko, Kagi etc.), indicators (SMA, EMA, MACD), oscillators (Stochastic, RSI), Fibonacci retracements etc.              
                        \item Hedging: In hand experience of hedging techniques (mainly with Nifty futures).               
                        \item Used data bases like Reuters, Moneycontrol, Screener, NSE portal, \& trading suites like TradeLab's Pi.                          
                        \item Portfolio management:Managed portfolios of an amount of about 12 Lacs with basic risk-management.
                      \end{itemize}
                    }
                    {Tomcat, Oracle DB, RichFaces, jQuery, Bootstrap, LESS, Hibernate, Spring, Eclipse, Maven}
 \emptySeparator
  \consultantexperience
  {April 2017}       {Research Intern}{French National Centre for Scientific Research}{Paris area}
  {June 2017}   {}{}
                    {
                      \begin{itemize}
                        \item Performed primary research while working one of the largest and next generation Global Astrophysics Project: The Cherenkov Telescope Array                             
                        \item Mathematically modeled the evolution function in C Programming language.         
                        \item Analysed results by comparing the data from H.E.S.S., Fermi-LAT (NASA), VERITAS                  
                      \end{itemize}
                    }
                    {\emph{WAS} 7, DB2, RichFaces, Infosphere Traceability Server, Hibernate, Ant}
  \emptySeparator
\end{experiences}
